Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-02-27 paper.tex
Some more notes
Intro work

\usepackage{lib/style/guthesis} % Must be the last package

\newtheorem{theorem}{Theorem}[section]
\newtheorem{adversary}{Adversary Model}

@@

People us the internet to communicate and share a variety of content. Some entities choose to censor internet connections. These entities may range from individual network administrators to a full nation-state. In this paper, we explore the state of censorship, existing circumvention systems, and we design and build a system which tackles several of the limitations present in state of the art systems. [LATER: Add xrefs to sections]

We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this discipline. We then explore the present theory behind approaches to censorship circumvention. We address the ethics of censorship circumvention as a field, and how the field originated and how that affects the current state of the field.

We then propose several ways to classify existing systems to allow for some comparison between them, and we then explore existing and past systems to understand where the field stands, and where limitations occur. We emphasize systems that are either cutting edge or in active use in the real world.

@@

\section{Networking concepts}

@@

\begin{figure}
\begin{center}
{\includesvg{figures/networking}}
\end{center}
\caption{A model of networking, sufficient for exploring censorship circumvention [TODO: Add final arrows, some sample traffic]}
\end{figure}

\section{What is censorship circumvention?}

@@

\subsection{Threat model and adversary}

@@

\begin{figure}
\begin{center}
{\includesvg{figures/networking}}
\end{center}
\caption{A model of networking, with our adversary model overlaid [TODO: Once networking diagram is finalized, add an adversary]}
\end{figure}

@@

\begin{figure}
\begin{center}
{\includesvg{figures/networking}}
\end{center}
\caption{A model of networking, with our adversary performing basic censorship [TODO: Once networking diagram is finalized, show blocking]}
\end{figure}

@@

@@

\subsubsection{Modeling collateral damage}

@@

\section{Real world observations}

[TODO - a bunch of case studies]

@@

@@

@@

\chapter{Conclusion}

@@

\appendices  % Indicates that appendices follow.
% If there's only one, use \appendix instead.

\chapter{Sample appendix}
SAMPLE
\section{Sample section}
SAMPLE

\chapter{Second sample appendix}
SAMPLE

>>>>

\usepackage{lib/style/guthesis} % Must be the last package
\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = black, %Colour of internal links
  citecolor   = black %Colour of citations
}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{question}{Research Question}
\newtheorem*{keyq}{Key Research Question}
\newtheorem{adversary}{Adversary Model}

@@

The internet has become a staple of the modern world, used by nearly every person on Earth.[CITE] The internet is a collection of independently managed networks which can route arbitrary traffic between said networks. It is built upon numerous \emph{protocols} which have been designed and iterated upon both academically and through practical usage over decades. Traffic on the internet travels from the edge of one network into another.\footnote{\emph{See} \ref{networking} for more on networking and key networking concepts.} This high level view loses some key context: networks are run by entities who have their own desires and are free to operate their network as they see fit. In an ideal world, all of these entities would run the same algorithms and would move traffic in a content-agnostic fashion, but we do not live in an ideal world. A variety of confounding factors result in a web that looks very different in practice from idealized theory: malicous entities use the web to perform attacks, bugs cause unforseen issues to arise, entities want to tightly control traffic and content in their network, among other complicating factors.

The more complicated web that actually exists leads to a variety of issues that don't arise in pure networking theory, one of which is \emph{censorship circumvention}.\footnote{\emph{See} \ref{circumvention} for our full definition and further discussion.} Censorship circumvention arises because some network-controlling entities choose to engage in censorhip. Censorship has become a loaded term in the current political context, and we do \emph{not} mean the coloquial usage of censorship. Censorship, as we discuss it, refers to entities censoring web traffic (either through complete blocking or other manipulation) at nodes (frequently routers) in the network(s) that they control. Censorship may be done for a variety of reasons - most censors will claim they are solely removing malicious traffic, however, an entity may operate their own definition of malicious which would differ from coloquial usage of the term. We see some entities that choose to block social media sites, news sources, or any site that they deem as block-worthy. Censors have a variety of justifications for their actions: economic protectionism, removing unsavory content, blocking dangerous content, maintaining law and order, and others. We see this and ask our key reasearch question:
\begin{keyq}
Can we circumvent censorship?
\end{keyq}
This is a very broad question - to be able to address it in a scientific manner we must refine it and break out some more specific and actionable research questions. To circumvent censorship, we must address what it is:

\begin{question}
What do existing censorship systems look like?
\end{question}

We explore previous work to answer this question.[XREF] [TODO: Add more] This allows us to refine our key question:

\begin{keyq}
Can we circumvent existing censorship systems? If so, how?
\end{keyq}

As we discussed above, we note that some entity is performing censorship - censorship is not occuring spontaneously. Systems are not deployed magically, and do not arise without a concerted action undertaken by an entity. This leads us to our next research question:

\begin{question}
Can we define an adversary and model their censorship systems?
\end{question}

Previous work has spent significant time defining adversaries in order to posit new methods of circumvention, and we define our adversary in a similar fashion. Our adversary has unlimited resources, constrained only by physics and algorithmic limitations.\footnote{\emph{See} \ref{adversary} for our full definition and further discussion.} In our model, we also assume there is at least 1 location \emph{not} under the control of any censoring adversary. Our theoretical adversary is informed by both real world observations and theories developped in prior work. In the real world, we frequently see adversaries perform basic censorship actions, such as blocking IPs and DNS resolutions. We also see adversaries taking more extreme actions, such as performing fingerprinting attacks or other techniques involving deep packet inspection (DPI).\footnote{\emph{See} \ref{real} for our exploration of real-world adversaries.} In theory, we see formulations that involved the adversary either attacking specific protocols [TODO e.g. xref Wang discussion] or employing a specific method of attack. [TODO: xref Salmon discussion] In prior work, most adversarial actions are discussed in a vacuum - rather than looking at how an adversary may choose the full setup of a censorship suite, adversary modelling focuses on an adversary trying to tackle just one method of circumvention, and the broader picture is ignored. We formulate a model for evaluating an adversaries actions that looks at the \emph{whole} of their censorship apparatus:\footnote{\emph{See} \ref{theory} for more details and the derivation.}

\begin{equation}
[TODO: insert the final equation after cleaning notation]
\end{equation}

This model of an adversary is a novel contribution and allows for rooting research in the field to both existing theory and the real world. With an adversary and adequate model defined, we can further refine the key research question tackled in this paper:

\begin{keyq}
Can we circumvent our adversaries censorship systems?
\end{keyq}

We cannot immeadiately answer this question - as we see in our model, an adversary has some utility function. Using both observations and a hypothetical, consider a utility function where an adversary does not care about blocking access to sites they deem legitimate (i.e., blocking an allowed site has a utility to the adversary of $0$), but they strongly do not want anyone to access a non-legitimate site (i.e. a user accessing a non-legitimate site has a utility of $-\infty$). This adversary would simply disable the internet. This would provide them with $0$ utility, which is their maximal utility. In fact, in some instances censors have had real-world utility functions that result in actions like this, though those instances have been short lived.[CITE] However, in practice, we see that no censor has continually provided 0 internet access - indicating that real world adversaries place a non-zero value on allowing access to legitimate sites, but they might place a very negative value on some non-legitimate sites. The key point is that, while we can come up with infinite theoretical utility functions, we should focus on real and realistically possible utility functions, leading us to one research question:

\begin{question}
What does a realistic utility function look like for a censor?
\end{question}

We rely on looking at previous work focusing on real world adversaries to tackle this question, as well as novel contemporary observations. We find that most censors, in most circumstances, wish to censor users while providing access to acceptable sites. We also see that censors frequently fail to block some traffic that they could block using some known methods. This brings us to the key concept of \emph{collateral damage}. A censor can employ censorship techniques to stop some traffic that they wish to stop, but many methods of censorship would result in shutting down access to some allowed traffic as a result of using those methods. We see several real world adversaries who employ some similar and some differing techniques, with varying defgrees of collateral damage. As such, we refine our key research question:

\begin{keyq}
Can we circumvent our adversaries censorship system, given a realistic adversarial utility function?
\end{keyq}

First, if we \emph{only} look at \emph{current} censorship apparatuses and real-world adversarial utility functions, we could conclude and say yes - based entirely on previous work. In practice, we see that the circumvention system Snowflake is currently working under all adversaries. However, while, for analysis sake, we fix a utility function at a given point in time, adversaries \emph{do} change their utility functions, and new censorship systems arise. Adversaries are frequently trying to develop new systems, and so we cannot assume a system will last indefinitely.\footnote{We note that a circumvention system which is provably able to survive could arise, however \emph{all} existing tools either do not have a strong scientific proof (e.g. Snowflake) or proofs are frequently constrained beyond a reasonable point (e.g. Obfs).} We choose to look ahead to an adversary either adopting a different, more constraining utility function or the development of a new censorship system that is more optimal than currently deployed systems. This leads us to our next research question:

\begin{question}
What might censorship look like in the near future?
\end{question}

We note that stronger censorship in the near future may emerge due to either a utility function less sensitive to collateral damage, or using a more advanced censorship system. We review related work and synthesize some possibilities for actions an adversary may take in the future. We focus on currently succesful circumvention techniques, and provide some methods of censorship an adversary may engage in to further restrict these systems using existing techniques that might increase collateral damage. We also explore censorship techniques, and we observe that deep packet inspection and bridge enumeration are the two broad techniques an adversary may use in a more advanced censorship system. We discuss some directions that these techniques may proceed in. [TODO: More] We use this to refine our overarching research question into an approachable question:

\begin{question}
Can we circumvent our adversaries existing or potential censorship systems, given a realistic adversarial utility function?
\end{question}

We address this question head on. We design and build a system to do this.

[TODO: Remove old intro]

@@

\section{Networking concepts}
\label{networking}

@@

\begin{figure}
\begin{center}
{\includesvg{figures/networking}}
\end{center}
\caption[Basic networking]{A model of networking, sufficient for exploring censorship circumvention [TODO: Add final arrows, some sample traffic]}
\end{figure}

\section{What is censorship circumvention?}
\label{circumvention}

@@

\subsection{Threat model and adversary}
\label{adversary}

@@

\begin{figure}
\begin{center}
{\includesvg{figures/networking}}
\end{center}
\caption[Basic networking, with an adversary]{A model of networking, with our adversary model overlaid [TODO: Once networking diagram is finalized, add an adversary]}
\end{figure}

@@

\begin{figure}
\begin{center}
{\includesvg{figures/networking}}
\end{center}
\caption[Basic networking, with an adversary performing censorship]{A model of networking, with our adversary performing basic censorship [TODO: Once networking diagram is finalized, show blocking]}
\end{figure}

@@

[TODO: Rework]

@@

@@

\section{Real world observations}
\label{real}

[TODO - a bunch of case studies]
 ,
[Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]

@@

\chapter{Theory}
\label{theory}

[TODO: Walk through one example using this]

@@

[TODO: Finish this section]

@@

\chapter{Conclusions}

@@

[Could use salmon stuff still, even if not perfect, especially since we are not an anonymity system]

[Killer app/other uses/etc]
